Specific leaf area explains difference in biomass partitioning between woody plant functional types

### 2014-08-08 manuscript/draftpaper.tex
more progress ....

\title{Leaf to stem biomass partitioning is explained by specific leaf area}

@@

@@

>>>>

\title{Specific leaf area explains difference in biomass partitioning between woody plant functional types}

@@

\section{Analyses}

A list of analyses to be included, either in the main text or as supporting information. We need to show all these bits to support the storyline.

\begin{enumerate}
  \item Leaf mass vs. aboveground biomass; line per species/studyName, colored by pft.
  \item Leaf mass / aboveground biomass vs. plant height; line per species/studyName, colored by pft.
  \item Barplot leaf mass / aboveground biomass at reference height with bootstrap CI, by pft (and vegetation type)
  \item Barplot leaf area / aboveground biomass at reference height with bootstrap CI, by pft (and vegetation type)
  \item Same ones but for leaf mass or leaf area vs. stem area (at BH or base).
  \item Ratio mass / stem area vs. SLA, ratio area / stem area vs. SLA, as estimated from random effects of fitted lme model.
  \item Root - shoot ratio, and barplots of pft/vegetation averages with bootstrap CI.
  \item Histogram of estimated effects at a reference height, by plant functional type, showing the variation between species. 
\end{enumerate}

@@

\begin{itemize}
  \item Removed deciduous gymnosperms, we have a few of those in BAAD (6 species / studyName combinations), but only one includes estimates of leaf area and mass. We did not attempt here to include SLA from another database (* although we can do this, we need to decide!).
\end{itemize}
